Preprocess

### 2023-12-07 src/preprocess.Rmd
regen pdfs
Add sex to preprocess

@@

```{r}
# Physicians cols to keep and rename for consistency
phy_cols <- c(
    "rowid",
    "death_age_group",
    "p1_icd",
    "p2_icd",
    "p1_recon_icd",
    "p2_recon_icd",
    "adj_icd"
)
phy_rename <- c(
    age_range = "death_age_group"
)
phy_adult_cols <- c(
    "rowid",
    "death_age_group",
    "p1_icd_cod",
    "p2_icd_cod",
    "p1_recon_icd_cod",
    "p2_recon_icd_cod",
    "adj_icd_cod"
)
phy_adult_rename <- c(
    age_range = "death_age_group",
    p1_icd = "p1_icd_cod",
    p2_icd = "p2_icd_cod",
    p1_recon_icd = "p1_recon_icd_cod",
    p2_recon_icd = "p2_recon_icd_cod",
    adj_icd = "adj_icd_cod"
)

@@

```{r}
df$physician <- df$physician %>%
    mutate(
        physician_icd10 = coalesce(
            adj_icd,
            p1_recon_icd,
            p1_icd
        ),
        is_agreed = if_else(
            is.na(p1_recon_icd) & is.na(p2_recon_icd) & is.na(adj_icd),
            TRUE,
            FALSE
        ),
        is_recon = if_else(
            !is.na(p1_recon_icd) | !is.na(p2_recon_icd),
            TRUE,
            FALSE
        ),
        is_adj = if_else(
            !is.na(adj_icd),
            TRUE,
            FALSE
        )
    ) %>%
    select(
        rowid,
        round,
        age,
        p1_icd,
        p2_icd,
        p1_recon_icd,
        p2_recon_icd,
        adj_icd,
        is_agreed,
        is_recon,
        is_adj,
        physician_icd10
    )
head(df$physician)
```

>>>>

```{r, echo=FALSE}
cat("R Version\n---")
R.version

cat("\nPackage Versions\n---")
cat(paste0("\ntidyverse ", packageVersion("tidyverse")))
```

@@

```{r}
# Physicians cols to keep and rename for consistency
phy_cols <- c(
    "rowid",
    "death_age_group",
    "sex_death",
    "p1_icd",
    "p2_icd",
    "p1_recon_icd",
    "p2_recon_icd",
    "adj_icd"
)
phy_rename <- c(
    sex = "sex_death",
    age_range = "death_age_group"
)
phy_adult_cols <- c(
    "rowid",
    "death_age_group",
    "sex_death",
    "p1_icd_cod",
    "p2_icd_cod",
    "p1_recon_icd_cod",
    "p2_recon_icd_cod",
    "adj_icd_cod"
)
phy_adult_rename <- c(
    age_range = "death_age_group",
    sex = "sex_death",
    p1_icd = "p1_icd_cod",
    p2_icd = "p2_icd_cod",
    p1_recon_icd = "p1_recon_icd_cod",
    p2_recon_icd = "p2_recon_icd_cod",
    adj_icd = "adj_icd_cod"
)

@@

```{r}
df$physician <- df$physician %>%
    mutate(
        physician_icd10 = coalesce(
            adj_icd,
            p1_recon_icd,
            p1_icd
        ),
        is_agreed = if_else(
            is.na(p1_recon_icd) & is.na(p2_recon_icd) & is.na(adj_icd),
            TRUE,
            FALSE
        ),
        is_recon = if_else(
            !is.na(p1_recon_icd) | !is.na(p2_recon_icd),
            TRUE,
            FALSE
        ),
        is_adj = if_else(
            !is.na(adj_icd),
            TRUE,
            FALSE
        )
    ) %>%
    select(
        rowid,
        round,
        age,
        age_range,
        sex,
        p1_icd,
        p2_icd,
        p1_recon_icd,
        p2_recon_icd,
        adj_icd,
        is_agreed,
        is_recon,
        is_adj,
        physician_icd10
    )
head(df$physician)
```
